Programs Performance Analysis Toolkit

### 2013-09-30 keynote/Keynote.tex
Remove unnecessary preambule
Add 2 slides on method

\documentclass{beamer}
\usepackage[T2A]{fontenc}
\usepackage[english,russian]{babel}
\usepackage[utf8x]{inputenc}

@@

@@

>>>>

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

@@

% Multi-slide enumeration
% http://tex.stackexchange.com/questions/55000/continuing-enumerate-counters-in-beamer
\newcounter{saveenumi}
\newcommand{\seti}{\setcounter{saveenumi}{\value{enumi}}}
\newcommand{\conti}{\setcounter{enumi}{\value{saveenumi}}}

\resetcounteronoverlays{saveenumi}

@@

\begin{frame}
\frametitle{Method of statistical programs performance analysis ''Velocitas''}

	\begin{enumerate}
		\item Perform a series of experiments on measuring time of program execution and form a set, $U$:
			\begin{equation*}
				U = \{ ( X_i, y_i ) \}, X_i = (x_{ij}, i \in [1;m], j \in [1;n])
			\end{equation*}
		$X_i$ --- features vector (CPU frequency, number of rows of processed matrix, etc.), $y_i$ --- response (execution time), $m$ --- number of experiments, $n$ --- number of features
		\seti
	\end{enumerate}

\begin{frame}
	\begin{enumerate}
		\conti
		\item Split the $U$ set into training sample $D$ and test sample $C$ by randomly assigning of 70\% of experiments to $D$
			\begin{eqnarray*}
				D &=& \{d_i | f_{rand}^I(d_i) > 0.3\}, \\
				d_i &=& (X_i, y_i), \\
				f_{rand}^I(d) &\in & [0:1], \\
				i &\in & [1;m], \\
				C &=& U \setminus D
			\end{eqnarray*}
		\seti
	\end{enumerate}
\end{frame}
